### 2018-07-16 experiments.tex
more fixes from reviewers

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault --- a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes, but effectively disabled some mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (\% of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  \comment{Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.}

@@

For GCC wrong code faults, the baseline chance two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric matched fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

>>>>

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault --- a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes, but effectively disabled the mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (\% of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization.  MUSEUM uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  \comment{Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.}

@@

For GCC wrong code faults, the baseline chance that two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric showed the same fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

### 2018-07-16 othertools.tex
more fixes from reviewers

\subsubsection{CoREBench Results} For the full data set in the paper \cite{Papadakis}, {\bf Repair} does not perform as well as MUSE and Metallaxis-FL, as expected.   It is only able to  rank a faulty line of code for 12 of 30 faults.  However, for these faults, it performs very well indeed, perfectly localizing 7 of the 12 (vs. 3 total perfect localizations for Metallaxis-FL and 4 for MUSE).  {\bf Repair} is uniquely best for 5 of the 12, and is tied for best for another 6; for the remaining fault, it performs better than Metallaxis-FL but worse than MUSE.  Table \ref{otherbugs} shows full results.  The fourth column shows, for those bugs where {\bf Repair} did not rank any faulty statement, how many statements {\bf Repair} proposed for a user to examine.  Note that in most cases if {\bf Repair} was not helpful it also provided little output to waste a user's time: it only once presented more than 3 statements to examine.   In practice, we only suggest using {\bf Repair} at all in cases where 1) there is at least one repairing mutant (not killed by any passing test) for a failing test and 2) there are multiple failing tests (whether from one or multiple faults).  When the Lines column shows a bold 0, it indicates there were no repairs (7 of the 30 faults).  The 7 faults meeting both requirements are bolded.  For 4 of these, {\bf Repair} produces a perfect localization, and for the other three, it produces no more than 2 non-faulty statements to examine.

\begin{table}
\caption{Fault localization for CoREBench faults}
\centering
{\scriptsize
\begin{tabular}{|c|c||c|c||c|c|}
\hline
& \#Failing & & & & \\
Fault & Tests & Repair & Lines & Metallaxis-FL & MUSE\\
\hline
{\bf Coreutils 1} & 2 & 1 & - & 1 & 1 \\
Coreutils 2 & 3 & - &  {\bf 0} & 86 & 186 \\
Coreutils 3 & 1 & 25 & - & 47 & 27 \\
Coreutils 4 & 1 & - &  {\bf 0} & 28 & 431 \\
{\bf Coreutils 5} & 5 & - &  2 & 4 & 7 \\
Coreutils 6 & 1 & - &  1 & 5 & 206 \\
Coreutils 7 & 1 & 1 & - & 5 & 9 \\
Coreutils 8 & 1 & - &  1 & 22 & 160 \\
{\bf Coreutils 9} & 5 & - &  1 & 10 & 157 \\
Coreutils 11 & 1 & - &  1 & 2 & 1 \\
Coreutils 12 & 2 & - & {\bf 0} & 6 & 9 \\
Coreutils 13 & 1 & - & {\bf 0} & 905 & 833 \\
Coreutils 14 & 1 & 14 & - & 19 & 11 \\
{\bf Coreutils 15} & 2 & 1 & - & 1 & 6 \\
Coreutils 16 & 1 & - & {\bf 0} & 569 & 447 \\
{\bf Coreutils 17} & 3 & - &  2 & 37 & 195 \\
Coreutils 18 & 1 & - &  3 & 27 & 3 \\
Coreutils 19 & 1 & 1 & - & 3 & 1 \\
{\bf Coreutils 20} & 7 & 1 & - & 12 & 3 \\
Coreutils 21 & 2 & - & {\bf 0} & 20 & 191 \\
{\bf Coreutils 22} & 2 & 1 & - & 6 & 2 \\
Findutils 27 & 1 & - &  9 & 12 & 6 \\
Findutils 32 & 1 & - &  1 & 73 & 70 \\
Findutils 33 & 1 & - &  3 & 10 & 30 \\
Findutils 35 & 1 & 1 & - & 1 & 1 \\
Findutils 36 & 1 & 9 & - & 9 & 19 \\
Findutils 37 & 1 & 11 & - & 22 & 34 \\
Grep 46 & 1 & - &  2 & 7 & 10 \\
Grep 47 & 1 & 4 & - & 4 & 4 \\
Grep 48 & 1 & - & {\bf 0} & 26 & 497 \\

>>>>

\subsubsection{CoREBench Results} For the full data set in the paper \cite{Papadakis}, {\bf Repair} does not perform as well as MUSE and Metallaxis-FL, as expected.   It is only able to  rank a faulty line of code for 12 of 30 faults.  However, for these faults, it performs very well indeed, perfectly localizing 7 of the 12 (vs. 3 total perfect localizations for Metallaxis-FL and 4 for MUSE).  {\bf Repair} is uniquely best for 5 of the 12, and is tied for best for another 6; for the remaining fault, it performs better than Metallaxis-FL but worse than MUSE.  Table \ref{otherbugs} shows full results.  The fourth column shows, for those bugs where {\bf Repair} did not rank any faulty statement, how many statements {\bf Repair} proposed for a user to examine.  Note that in most cases if {\bf Repair} was not helpful it also provided little output to waste a user's time: it only once presented more than 3 statements to examine.   In practice, we only suggest using {\bf Repair} at all in cases where 1) there is at least one repairing mutant (not killed by any passing test) for a failing test and 2) there are multiple failing tests (whether from one or multiple faults).  When the Stmts column shows a bold 0, it indicates there were no repairs (7 of the 30 faults).  The 7 faults meeting both requirements are bolded.  For 4 of these, {\bf Repair} produces a perfect localization, and for the other three, it produces no more than 2 non-faulty statements to examine.

\begin{table}
\caption{Fault localization for CoREBench faults}
\centering
{\scriptsize
\begin{tabular}{|c|c||c|c||c|c|}
\hline
& \#Failing & & & & \\
Fault & Tests & Repair & Stmts & Metallaxis-FL & MUSE\\
\hline
{\bf Coreutils 1} & 2 & 1 & - & 1 & 1 \\
Coreutils 2 & 3 & - &  {\bf 0} & 86 & 186 \\
Coreutils 3 & 1 & 25 & - & 47 & 27 \\
Coreutils 4 & 1 & - &  {\bf 0} & 28 & 431 \\
{\bf Coreutils 5} & 5 & - &  2 & 4 & 7 \\
Coreutils 6 & 1 & - &  1 & 5 & 206 \\
Coreutils 7 & 1 & 1 & - & 5 & 9 \\
Coreutils 8 & 1 & - &  1 & 22 & 160 \\
{\bf Coreutils 9} & 5 & - &  1 & 10 & 157 \\
Coreutils 11 & 1 & - &  1 & 2 & 1 \\
Coreutils 12 & 2 & - & {\bf 0} & 6 & 9 \\
Coreutils 13 & 1 & - & {\bf 0} & 905 & 833 \\
Coreutils 14 & 1 & 14 & - & 19 & 11 \\
{\bf Coreutils 15} & 2 & 1 & - & 1 & 6 \\
Coreutils 16 & 1 & - & {\bf 0} & 569 & 447 \\
{\bf Coreutils 17} & 3 & - &  2 & 37 & 195 \\
Coreutils 18 & 1 & - &  3 & 27 & 3 \\
Coreutils 19 & 1 & 1 & - & 3 & 1 \\
{\bf Coreutils 20} & 7 & 1 & - & 12 & 3 \\
Coreutils 21 & 2 & - & {\bf 0} & 20 & 191 \\
{\bf Coreutils 22} & 2 & 1 & - & 6 & 2 \\
Findutils 27 & 1 & - &  9 & 12 & 6 \\
Findutils 32 & 1 & - &  1 & 73 & 70 \\
Findutils 33 & 1 & - &  3 & 10 & 30 \\
Findutils 35 & 1 & 1 & - & 1 & 1 \\
Findutils 36 & 1 & 9 & - & 9 & 19 \\
Findutils 37 & 1 & 11 & - & 22 & 34 \\
Grep 46 & 1 & - &  2 & 7 & 10 \\
Grep 47 & 1 & 4 & - & 4 & 4 \\
Grep 48 & 1 & - & {\bf 0} & 26 & 497 \\
